### 2018-03-14 Writing/Thesis/content/chapter-approach.tex
integrate comments part five

In general, the aim is to predict a ranking of algorithms based on properties, or meta features of a data set. This means, that as training data for a ranking approach (ranker), a number of performance values of classifiers need to be recorded on data sets in a first pre-processing phase, for which also meta features are to be computed. The table of this collected data is illustrated in Table \ref{tab:performanceValues}, for n meta features, k classifiers and m data sets. This approach to ranking is realized here, as pointed out before, in a regression-based and preference-based approach, which are explained in detail in the following sections.

@@

\subsection{Regression-Based Ranking}
% How is the regression ranking done
One possibility to derive a ranking of classifiers from this information when given a new data set is to use regression models. The idea is to use separate regression models to predict a performance value for each classifier, and to subsequently derive an ordering from these predictions. This is done by splitting the data set compiled beforehand (see Tab. \ref{tab:performanceValues}) into separate data sets that each contain all meta features for all data sets, but only the performance values of one classifier, as illustrated in Table \ref{tab:regressionTables}. The target feature on these individual data sets, the performance value of the classifier, is a numeric value, and thus, a regression model can be trained on each of them. All regression models therefore try to learn the target function \textit{meta features}$\rightarrow$\textit{performance value} for their respective classifier. Hence, for a query instance, here represented by a new data set, the first step is to compute the meta features. Afterwards, these are fed into each regression model and the predicted performance value for each classifier is saved. In a second step, the classifiers are ordered according to the predictions. This generation of a ranking is presented in Figure \ref{fig:regression_ranker_model}.

@@

\subsection{Preference-Based Ranking}
% How is the preference ranking done
The second possibility considered in this context is using preference learning to predict a ranking. Each instance of the data set generated beforehand (see Tab. \ref{tab:performanceValues}) contains meta feature information for the considered data set and performance values of all classifiers. Similar to the regression alternative, the performance values can be converted to preference information by sorting the corresponding classifiers by their performance values for each data set. This leads to an ordering of classifiers associated with each instance, and implies that the preference learning task at hand is label ranking. In this case, there exists only one label ranking model which is fed the computed meta data for a new data set and returns an ordering of classifiers, which is depicted in Figure \ref{fig:preference_ranker_model}. Thereby, it attempts to learn the mapping from meta features to an ordering of classifiers directly.

@@

\section{Implementation}
In general, all implementations for the approach are carried out in Java, particularly Java 8. However, some additional packages were used, which are pointed out briefly. For the implementation of the regression models, WEKA was used, a popular libary of machine learning algorithms that includes algorithms for classification, regression, and provides help in the evaluation of these learning algorithms \cite{hall2009weka}. Regarding the preference algorithms, the jPL framework was used \cite{intelligent2017jpl}. The jPL framework is a Java framework for the evaluation of preference learning algorithms, it implements several tasks from the context of preference learning, including label ranking, and also provides a representation for data sets that contain label ranking information. The list of meta features used is taken from OpenML \cite{OpenML2013}, a website that not only provides a large number of openly accessible data sets, but also records performance values of learning algorithms on these data sets, and features properties of data sets. Thus the meta features were calculated with the help of an implementation provided by OpenML in its Evaluation Engine \cite{openMLEvaluationEngine}; the full list of meta features is included in Table \ref{tab:metaFeatureDetails} in the Appendix.

>>>>

In general, the aim is to predict a ranking of algorithms based on properties, or meta features of a data set. This means, that as training data for a ranking approach (ranker), a number of performance values of classifiers need to be recorded on data sets in a first pre-processing phase, for which also meta features are to be computed. The table of this collected data is illustrated in Table \ref{tab:performanceValues}, for n meta features, k classifiers and m data sets. This approach to ranking is realized here, as pointed out before, in a regression-based and preference-based variant, which are explained in detail and compared briefly in the following sections.

@@

\subsection{Regression-Based Ranking}
% How is the regression ranking done
One possibility to derive a ranking of classifiers from this information when given a new data set is to use regression models. The idea is to use separate regression models to predict a performance value for each classifier, and to subsequently derive an ordering from these predictions. The training of the ranker is done by splitting the data set compiled beforehand (see Tab. \ref{tab:performanceValues}) into separate data sets that each contain all meta features for all data sets, but only the performance values of one classifier, as illustrated in Table \ref{tab:regressionTables}. The target feature on these individual data sets, the performance value of the classifier, is a numeric value, and thus, a regression model is trained on each of them. All regression models therefore try to learn the target function \textit{meta features}$\rightarrow$\textit{performance value} for their respective classifier. After the regression models have been trained for each classifiers, the training of the ranker is finished. For a query instance, here represented by a new data set, the first step is to compute the meta features. Afterwards, these are fed into each regression model and the predicted performance value for each classifier is saved. In a second step, the classifiers are ordered according to the predictions. This generation of a ranking is presented in Figure \ref{fig:regression_ranker_model}.

@@

\subsection{Preference-Based Ranking}
% How is the preference ranking done
The second possibility considered in this context is using preference learning to predict a ranking. Each instance of the data set generated beforehand (see Tab. \ref{tab:performanceValues}) contains meta feature information for the considered data set and performance values of all classifiers. The performance values can be converted to preference information by sorting the corresponding classifiers by their performance values for each data set, similar to the prediction step of the regression alternative, which is the first step of building the ranker. This leads to an ordering of classifiers associated with each instance, and implies that the preference learning task at hand is label ranking. In this case, in contrast to the regression-based approach, there exists only one model, a label ranking model. To complete the training of the ranker, this model is built with the training data that has been converted to a label ranking data set in the previous step. To make predictions, the computed meta data for a new data set is fed to this model, which consequently returns an ordering of classifiers, which is depicted in Figure \ref{fig:preference_ranker_model}. Thereby, it attempts to learn the mapping from meta features to an ordering of classifiers directly.

@@

\subsection{Comparison}

While both of the ranking approaches above are used for the same purpose of ranking classification algorithms, they differ in some aspects that are interesting to point out. First, they theoretically do not require the same kind of training data. While the preference ranker only needs rankings, the regression ranker requires the exact performance data of all considered classifiers on the data sets. Although here it does not make a difference, since the performance values are computed anyways as the regression ranker utilizes them, in cases where only rankings of classifiers for a data set are known or performance values are estimated in a way that is biased, but has the same bias for all classifiers, so that the ranking is not influenced, this may be an advantage. Furthermore this leads to the curios case that training examples for the regression ranker are not directly samples from the target function the ranker learns. The target function for the regression ranker (as for the preference ranker) maps meta features of a data set to a ranking. However, for the regression ranker, the training examples have to include the actual performance values, meaning that they are of the form (\textit{meta features}, \textit{performance values}).

Also, the approaches behave differently regarding the addition (or deletion) of a data set or classifier. If a classifier is added, for the regression-based approach, a regression model needs to be added to the ranker. Therefore, performance values for the classifier for the data set would need to be available or have to be computed anew. For the preference-based approach, however, the whole label ranking model, therefore the whole ranker, would need to be trained again, as for every data set, the ranking of classifiers has changed. Here a regression ranker conceptually has an advantage. The deletion of a classifier is much simpler: for the regression-based ranker, one regression model has to be deleted, which does not affect the other models, and in the case of the preference ranker, in the rankings produced by the label ranking model the unwanted classifier can just be removed from the rankings.

For the addition of a data set, the situation is unfavorable for both rankers. Since a new training example would be added to each regression model, they all need to be trained again on the now extended training data. For the preference ranker, likewise a new training example is added to the training data, and a new model has to be trained. The same is the case for the deletion of a data set.

Regarding training and prediction, conceptually, the preference ranker has the advantage that it both only needs to build one model and to have one model make a prediction for a new data set. On the other hand, the regression ranker needs to build as many models as there are classifiers in consideration, and also have as many models predict a performance value for their respective classifiers, which then also have to be turned into a ranking. In general, this indicates a better scalability of the preference-based approach regarding the number of classifiers (unless they are to be added dynamically) and data sets, although of course this also depends on the specific algorithms used.

\section{Implementation}

The implementation of the rankers themselves is relatively straightforward with the theory of the previous sections in mind. However, since the goals for his thesis includes the development of an AutoML tool that returns a ranking of classification algorithms when given a data sets, the scope of the implementation goes beyond the ranking algorithms, including also pre-processing steps and means of evaluation for the rankers, relevant parts of the implementation are described in the following paragraphs; it is notable that all implementations were carried out in Java, particularly Java 8.

As mentioned before, the implementations of the ranking approaches are relatively close to the theory and will therefore not be described in detail, except for a few notable parts. First, since the tool relies on external libraries for the learning algorithms, these need to be pointed out. For the implementation of the regression models, WEKA was used, a popular libary of machine learning algorithms that includes algorithms for classification, regression, and provides help in the evaluation of these learning algorithms \cite{hall2009weka}. Regarding the preference algorithms, the jPL framework was used \cite{intelligent2017jpl}. The jPL framework is a Java framework for the evaluation of preference learning algorithms, it implements several tasks from the context of preference learning, including label ranking, and also provides a representation for data sets that contain label ranking information.

Furthermore, so far, the descriptions of the `performance measure' used for the classifiers, that is the measure according to which the classifiers are ranked, for example the error rate or predictive accuracy, have been kept non-specific. Likewise, although the measure used in the evaluation in this thesis is predictive accuracy, the implementation has been kept general to allow any measure to be used with the rankers, as long as it is numeric.

Another fact worth mentioning regarding the implementation of the rankers is that both the regression-based approach and the preference-based approach are implemented in a way that abstract superclasses handle the data set conversions and other necessary tasks, so that it is very easy to add a new ranker implementation. For example, to create a new ranker that uses random forest as a regression model for each classifier, it is only necessary to override a method called \texttt{buildRegressionModels} which has the classifiers mapped to the training data necessary for the regression model of each classifier as a parameter and is responsible for the generation of the regression models. How this method is implemented in the case of random forest is illustrated in Figure \ref{lst:randomForest}. Here we can see that the regression model that has been acquired by training on the provided data is saved together with the classifier for which it predicts performance values. Later, this model is used to predict the performance value of that specific classifier.

\begin{figure}
\begin{lstlisting}
@Override
protected void buildRegressionModels
			(Map  Classifier, Instances> train) 
			throws Exception {
	regressionModels = new HashMap<Classifier,Classifier>();
	for (Classifier classifier : train.keySet()) {
		RandomForest forest = new RandomForest();
		forest.buildClassifier(train.get(classifier));
		regressionModels.put(classifier, forest);
	}
}
\end{lstlisting}
\caption{A source code excerpt for a ranker based on the random forest algorithm.}
\label{lst:randomForest}
\end{figure}

Last, while the computation of the meta features is included in the workflow of a ranker in the theoretical explanations of the previous sections, meta features are calculated separately in the implementation since it is a repeating task, to speed up the evaluation of classifiers. The list of meta features used is taken from OpenML \cite{OpenML2013}, a website that not only provides a large number of openly accessible data sets, but also records performance values of learning algorithms on these data sets, and features properties of data sets. Thus the meta features were calculated with the help of an implementation provided by OpenML in its Evaluation Engine \cite{openMLEvaluationEngine}; the full list of meta features is included in Table \ref{tab:metaFeatureDetails} in the Appendix. Like the choice which classifier and performance measure to use, the choice of which meta features to be used in the implementation can be changed flexibly.

In addition to this ranking functionality, methods for the evaluation of both classifiers and rankers are implemented. Although WEKA offers capabilities for the evaluation of classifiers, additional functionality had to be added, as for example the desired estimation procedure of stratified Monte Carlo cross-validation was not supported by WEKA at the time of the implementation. Furthermore, since for the evaluation of the rankers (to build the table depicted in Tab. \ref{tab:performanceValues}), many classifiers had to be evaluated on a large number of data sets, an efficient way to execute this task was needed. This was realized by enabling the tool to take a number of jobs, consisting of classifiers and data sets, as command-line parameters, which enables execution for example on a data mining cluster. For the evaluation of rankers, the functionality needed to be built without the help of existing frameworks, and was realized in a similar way to the implemented evaluation of WEKA classifiers. It was also implemented such that after a ranker has been trained once, it can be evaluated regarding a number of different measures, to speed up the evaluation process.

Apart from the functionality described above, the implementation includes some useful recurring functions from the context of handling data sets and classifiers in the context of WEKA and OpenML. To give a general idea how the tool is structured, an overview of the package structure is given in Fig. \ref.

\begin{figure}
\includegraphics[width=\textwidth]{gfx/Package_Structure.png}
\caption{An overview of the package structure of the tool.}
\label{fig:package_overview}
\end{figure}

### 2018-03-14 Writing/Thesis/content/chapter-evaluation.tex
integrate comments part five

Table \ref{tab:evaluationResults} shows the results of the evaluation regarding the accuracy of returned rankings, with the best mean values and significant differences emphasized as described in the caption of the table. When looking at these results, it must first be noted that positive findings regarding the Kendall rank correlation can be reported. For the full set of meta data, six out of the eight implemented alternatives outperform the baseline, all of them significantly, as can be learned from Table \ref{tab:significanceResults}, which shows the results of the significance tests according to the p-value for the Mann-Whitney U. Of all rankers, RandomForest has the highest rank correlation with a value of 0.495. In contrast, the two approaches that did not overtake the baseline, the InstanceBased ranker in the default configuration and the PairwiseComparison ranker, show a significant disadvantage compared to the baseline, and thus also compared to the other ranking approaches. Especially the latter approach has a very low rank correlation, that with a mean value of 0.014 shows almost no correlation with the correct ranking. Regarding performance loss, only the LinearRegression and RandomForest ranker show a significant advantage, with all label ranking approaches except for the InstanceBased ranker with Kemeny-Young rank aggregation having a significant disadvantage in contrast. Here, an advantage of the regression-based approach in general is indicated, although the best value with a loss of 3.097 (achieved by the RandomForest ranker) is still fairly high, depending on the data set one considers. Moving on to B3L, the picture largely remains the same, except that surprisingly, the REPTree ranker now also has a significant advantage over the baseline. The lowest value here again is achieved by the RandomForest ranker with a mean B3L of 1.308, in comparison to 2.440 for the best algorithm baseline. These values are illustrated in Figure \ref{fig:lossGraphics}, with a scatter plot for individual B3L values on the data sets.

As for the rank correlation most of the rankers had a significant advantage over the baseline, it is interesting to compare them among each other. From Table \ref{tab:evaluationResults} it is clear that the regression-based rankers are superior to the preference-based rankers, and this advantage is significant, as the weakest of the regression rankers, the REPTree ranker, is still significantly better than the strongest label ranking approach, the InstanceBased ranker with Kemeny-Young rank aggregation ($p \approx 4.305E-6$). Out of the four regression rankers, three approaches are furthermore significantly better than the REPTree ranker.

@@

\tikzsetnextfilename{LossGraphics}
\begin{figure}
%\pgfplotsset{width=\textwidth}
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}
\begin{axis}[
	title=regular scale,
	height=\textwidth,
	width=\textwidth,
	ylabel={B3L}, 
	xlabel={Data Set},
]
\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
\addplot [mark=*,only marks,mark size=1pt,uniaccentblue] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/RandomForestRanker_metaData_small_allPerformanceValues.csv};
\addplot [very thick,mark=none,black,samples=2,domain=0:450]{2.440};
\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{1.308};
\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{0};
\legend{BestAlgorithm, RandomForest, BestAlgorithm (mean), RandomForest (mean)}
\end{axis}
\end{tikzpicture}%
~%
%
\begin{tikzpicture}
\begin{axis}[
	title=log scale (base 2),
	height=\textwidth,
	width=\textwidth,
	ylabel={B3L}, 
	xlabel={Data Set},
	ymode=log,
	log basis y={2}
]
\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
\addplot [mark=*,only marks,mark size=1pt,uniaccentblue] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/RandomForestRanker_metaData_small_allPerformanceValues.csv};
\addplot [very thick,mark=none,black,samples=2,domain=0:450]{2.440};
\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{1.308};
\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{0};
\legend{BestAlgorithm, RandomForest, BestAlgorithm (mean), RandomForest (mean)}
\end{axis}
\end{tikzpicture}
}
\caption{The B3L for the baseline compared to the random forest ranker (full meta data).}
\label{fig:lossGraphics}
\end{figure}

@@

Table \ref{tab:metaFeatureTimes} shows the times required for the computation of groups of meta features as discussed in Chapter \ref{sec:approach}. As can be taken from the table, the computation of the full meta features takes approximately 135 milliseconds on average, while the simple meta features without probing add approximately 3 milliseconds to the prediction times on average. Regarding these computation times it is also notable that among the probing meta feature groups, some are considerably more expensive than others, so that in the future it might be sensible to consider only light probing with probing meta feature groups that are not as expensive.

>>>>

Table \ref{tab:evaluationResults} shows the results of the evaluation regarding the accuracy of returned rankings, with the best mean values and significant differences emphasized as described in the caption of the table. When looking at these results, it must first be noted that positive findings regarding the Kendall rank correlation can be reported. For the full set of meta data, six out of the eight implemented alternatives outperform the baseline, all of them significantly, as can be learned from Table \ref{tab:significanceResults}, which shows the results of the significance tests according to the p-value for the Mann-Whitney U. Of all rankers, RandomForest has the highest rank correlation with a value of 0.495. In contrast, the two approaches that did not overtake the baseline, the InstanceBased ranker in the default configuration and the PairwiseComparison ranker, show a significant disadvantage compared to the baseline, and thus also compared to the other ranking approaches. Especially the latter approach has a very low rank correlation, that with a mean value of 0.014 shows almost no correlation with the correct ranking.

Regarding performance loss, meaning much worse the performance of the first recommended algorithm is in comparison to the actual best algorithm on the data set, as defined in Chapter \ref{sec:fundamentals}, only the LinearRegression and RandomForest ranker show a significant advantage, with all label ranking approaches except for the InstanceBased ranker with Kemeny-Young rank aggregation having a significant disadvantage in contrast. Here, an advantage of the regression-based approach in general is indicated, although the best value with a loss of 3.097 (achieved by the RandomForest ranker) is still fairly high, depending on the data set one considers.

Moving on to B3L, the picture largely remains the same, except that surprisingly, the REPTree ranker now also has a significant advantage over the baseline. The lowest value here is achieved by the inearRegression ranker with a mean B3L of 1.267, in comparison to 2.440 for the best algorithm baseline. These values are illustrated in Figure \ref{fig:lossGraphics}, with a scatter plot for individual B3L values on the data sets. In this figure, we can observe that, for a large number of data sets, the B3L is actually 0, namely 206 data sets for the BestAlgorithm ranker and 248 for the RandomForest ranker, which corresponds to 46\% and 55\% of the 448 data sets used in the evaluation. The main portion of the remaining data points is situated between 0.25 and 8 for the RandomForestRanker, and 0.5 and 16 for the BestAlgorithm ranker, with few exceptions.

As for the rank correlation most of the rankers had a significant advantage over the baseline, it is interesting to compare them among each other. From Table \ref{tab:evaluationResults} it is clear that the regression-based rankers are superior to the preference-based rankers, and this advantage is significant, as the weakest of the regression rankers, the REPTree ranker, is still significantly better than the strongest label ranking approach, the InstanceBased ranker with Kemeny-Young rank aggregation, as indicated by a p-value of 4.305E-6. Out of the four regression rankers, three approaches are furthermore significantly better than the REPTree ranker.

@@

\tikzsetnextfilename{LossGraphics}
\begin{figure}
%\pgfplotsset{width=\textwidth}
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}
\begin{axis}[
	title=regular scale,
	height=\textwidth,
	width=\textwidth,
	ylabel={B3L}, 
	xlabel={Data Set},
]
\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
\addplot [mark=*,only marks,mark size=1pt,uniaccentblue] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/RandomForestRanker_metaData_small_allPerformanceValues.csv};
\addplot [very thick,mark=none,black,samples=2,domain=0:450]{2.440};
\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{1.308};
\legend{BestAlgorithm, RandomForest, BestAlgorithm (mean), RandomForest (mean)}
\end{axis}
\end{tikzpicture}%
~%
%
\begin{tikzpicture}
\begin{axis}[
	title=log scale (base 2),
	height=\textwidth,
	width=\textwidth,
	ylabel={B3L}, 
	xlabel={Data Set},
	ymode=log,
	log basis y={2}
]
\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
\addplot [mark=*,only marks,mark size=1pt,uniaccentblue] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/RandomForestRanker_metaData_small_allPerformanceValues.csv};
\addplot [very thick,mark=none,black,samples=2,domain=0:450]{2.440};
\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{1.308};
\legend{BestAlgorithm, RandomForest, BestAlgorithm (mean), RandomForest (mean)}
\end{axis}
\end{tikzpicture}
}
\caption{The B3L for the baseline compared to the random forest ranker (full meta data).}
\label{fig:lossGraphics}
\end{figure}

@@

Table \ref{tab:metaFeatureTimes} shows the times required for the computation of groups of meta features as discussed in Chapter \ref{sec:approach}. As can be taken from the table, the computation of the full meta features takes approximately 135 milliseconds on average, while the simple meta features without probing add approximately 3 milliseconds to the prediction times on average, which is already a difference of factor 45, which is quite large especially considering the fact that only light data sets, restricted in the number of features and instances, were used. To emphasize this difference, the meta features were calculated for the popular MNIST data set \cite{mnist}, which contains pictures of handwritten digits in a 28 by 28 pixel resolution, resulting in 784 features, plus the target feature. The data set contains 70.000 different pictures. For the computation of the full set of meta features, 4 hours and 51 minutes were needed, out of which only 24 seconds were needed for the reduced set of meta features, a difference of factor 735. Regarding these computation times it is also notable that among the probing meta feature groups, some are considerably more expensive than others, so that in the future it might be sensible to consider only light probing with probing meta feature groups that are not as expensive.

### 2018-03-14 Writing/Thesis/content/chapter-fundamentals.tex
integrate comments part five

In formal terms, the gardener is searching for an unknown \textit{target function} $f:X \rightarrow Y$ from the input space $X$ to the output space $Y$ \cite{abu2012learning} that represents an ideal way of identifying iris species. $X$ denotes the possible inputs, in this case all combinations of the four features that have been defined, whereas $Y$ are the outputs, here the species of iris plant. The examples that the gardener recorded are samples $(x_1,y_1),(x_2,y_2),\dots,(x_n,y_n)$ from $f$ such that $f(x_i)=y_i$. These tuples form a data set $D$ which is one of all possible data sets $\mathbb{D}$ for the problem. The gardener then choose a specific approximation $g:X \rightarrow Y,g\approx f$, the decision tree they built, from the hypothesis space $H$, which in this case consists of possible decision trees. The learning algorithm itself thus maps a data set to a hypothesis from the hypothesis space and can be defined as $A:\mathbb{D}\rightarrow H$. An overview of this learning problem is provided in Figure \ref{fig:learning_problem}.

@@

To find out how well a classifier performs, it first needs to be decided which measure to consider. There are a few possibilities for this, however in this thesis the term performance measure refers to the predictive accuracy of a classifier, that is the percentage of classes that a classifier correctly identified in a given data set. But since using the whole data set to train a classifier (build a model), would skew the analysis - the classifier has already `seen' these examples - a method for dividing data sets into train and test sets is needed.

@@

An alternative to using a stratified split is using a method called leave-one-out. This method essentially is, for a data set with n instances, n-fold cross-validation (not stratified, naturally). This means that the algorithm is trained on n-1 instances and evaluated on the instance that has been left out.

@@

@@

\begin{table}
\begin{tabularx}{\textwidth}{X | X | X | X | X}
			& $A_1$	& $A_2$	& $A_3$	& $A_4$ \\\hline
error rate	& 0.1	& 0.7	& 0.3	& 0.4	\\
rank			& 2		& 4		& 1		& 3	
\end{tabularx}
\caption{An exam.}
\label{tab:lossTable}
\end{table}

>>>>

In formal terms, the gardener is searching for an unknown \textit{target function} $f:X \rightarrow Y$ from the input space $X$ to the output space $Y$ \cite{abu2012learning} that represents an ideal way of identifying iris species. $X$ denotes the possible inputs, in this case all combinations of the four features that have been defined, whereas $Y$ are the outputs, or the target feature of the data set, here the species of iris plant. The examples that the gardener recorded are samples $(x_1,y_1),(x_2,y_2),\dots,(x_n,y_n)$ from $f$ such that $f(x_i)=y_i$. These tuples form a data set $D$ which is one of all possible data sets $\mathbb{D}$ for the problem. The gardener then choose a specific approximation $g:X \rightarrow Y,g\approx f$, the decision tree they built, from the hypothesis space $H$, which in this case consists of possible decision trees, and in general contains candidate formulas considered by the learning algorithm. The learning algorithm itself thus maps a data set to a hypothesis from the hypothesis space and can be defined as $A:\mathbb{D}\rightarrow H$. An overview of this learning problem is provided in Figure \ref{fig:learning_problem}.

@@

To find out how well a classifier performs, it first needs to be decided which measure to consider. There are a few possibilities for this, however in this thesis the term performance measure refers to the predictive accuracy of a classifier, that is the percentage of classes that a classifier correctly identified in a given data set. But since using the whole data set to train a classifier (build a model) and consequently test it, would skew the analysis - the classifier has already `seen' these examples - a method for dividing data sets into train and test sets is needed.

@@

An alternative to using a stratified split is using a method called leave-one-out. This method essentially is, for a data set with n instances, n-fold cross-validation (not stratified, naturally). This means that the algorithm is trained on n-1 instances and evaluated on the instance that has been left out. Since this method is executed n times on a data set with n instances, whereas for example 10-fold (stratified) cross-validation is always only executed ten times, it is computationally more expensive. This is especially the case for larger data sets, because generally, the time for training a classifier is increased with the number of training examples. However, as the number of training examples increases, the estimated accuracy of the classifier approaches the accuracy that it would achieve on the entire population (assuming that the samples are independent and not biased), making it desirable to have as many training examples as possible. Therefore, leave-one-out tends to be less biased than the (usually more negatively biased) variant of using k-fold cross-validation with a relatively small k \cite{kohavi1995study}. On the other hand, this leads to a higher variance of the estimates. So apart from considering the computational expense when choosing k, one has to think about the bias-variance trade-off.

@@

For illustration, once again the gardener example is used. Previously, the gardener has expressed their preference for the three different iris species of iris plants with the ranking [2,3,1] (see Tab \ref{tab:ranking_vs_ordering}). Suppose a different gardener instead has the preferences [3,2,1], and one wants to know to what degree they agree. To compute the Kendall rank correlation coefficient, first, the first position of both rankings would be the compared with the second positions, that is (2,3) with (3,2). This pair is discordant. The next pair, (2,3), (1,1), is concordant, and the last pair, (3,2), (1,1) is concordant as well. As there are no ties, this results in a correlation of $\frac{2-1}{3}=\frac{1}{3}$, indicating a slight agreement.

@@

\begin{table}
\begin{tabularx}{\textwidth}{X | X | X | X | X}
Algorithm	& $A_1$	& $A_2$	& $A_3$	& $A_4$ \\\hline
Error Rate	& 0.1	& 0.7	& 0.3	& 0.4	\\
Rank			& 2		& 4		& 1		& 3	
\end{tabularx}
\caption{An exam.}
\label{tab:lossTable}
\end{table}
